### 2015-03-18 paper_10_intro.tex
updates the chapter 1 this work to this dissertation

    This work 
    provides a technique for a Software Development Organization (SDO)
    \nomenclature{SDO}{Software Development Organization}to create
    a single number score which indicates the overall performance
    of the organization. The
    score is based upon data collected for 5 key result indicators
    of an SDO: quality, availability,
    satisfaction, schedule, and requirements.  It is not meant
    to be comparative between organizations, but to 
    form a historical baseline for a specific organization.  The single
    number is targeted for upper-level management whom need a quick
    and simple strategy to evaluate the performance of the organization.

@@

    SDOs need a framework to define
    what measurements should be tracked and how those measurements
    should be reported.  The Cumulative Result Indicator (CRI)
    \nomenclature{CRI}{Cumulative Result Indicator}
    framework provides a solid foundation
    for a consistent evaluation.  CRI analyzes the historical performance
    of an SDO
    to create a baseline in order to provide a broad
    view of the overall organization.  It is common for software development
    organizations to measure and focus soley on the source code
    being produced.  However, an SDO does more
    than just produce source code.  There is documentation to be
    written, testcases to be created, systems to be deployed, and
    decisions to be made.  The framework provides an evaluation
    of the overall SDO, not just the
    source code.

@@

        \item[Application] - a software system or a collection of other applications 
        \item[Release] - A collection of projects being put in production on a specified date
        \item[Project] - A body of work involving zero or more applications in preparation for a release 
        \item[SIT] (Systems Integration Testing) - The initial step of testing
            after the development phase of the SDLC.  This is typically 
            performed by members of the SDO.  It is validation that all the
            software components function together as expected.
            \nomenclature{SIT}{Systems Integration Testing} 
        \item[UAT] (User Acceptance Testing) - The final step of testing
            when a select few members of the user group are invited to
            validate the software system. Once validation has occured for
            UAT, the software system is ready to proceed to production
            \nomenclature{UAT}{User Acceptance Testing} 
        \item[PROD] (Production) - The software has been released to the 
        final audience. \nomenclature{PROD}{Production} 
        \item[defect] ``A software defect is a bug or error that causes
                    software to either stop operating or to produce
                    invalid or unacceptable results'' as quoted from Capers Jones
                \cite{Jones2009}.  It is important to mention that even though defects are typically 
                found in the computer code, a defect should not be isolated to just code.   
                A poorly written requirement or missed test cases can 
                both be considered a defect.  Other common names for a defect 
                are: bug, error, fault, or ticket.
    \end{description}

@@

    \begin{description}
        \item[CMMI MATURITY LEVEL 1 - INITIAL]
            A maturity level 1 organization consists of an
                adhoc and chaotic processes.  While working
                products are still produced, the results are 
                often over budget and behind schedule.  A level
                1 organization will also have difficulties 
                repeating a process with the same degree of 
                success.  These organizations typically rely 
                on the heroic efforts of certain individuals.

@@

    A visual description of the CMMI maturity levels can be seen in Figure \ref{fig:cmmi}.  
    While CMMI-Dev does provide an excellent framework for improving a process, it
    is wholely focused on process improvement.  It does not provide guidelines
    for evaluating the final product.  
    Also, it does not provide a specify mechanism for evaluating
    or scoring the progression through the maturity levels.  
    An indicator is still needed to quantify the overall 
    performance of an organization, not
    just the compliance to standard processes.

@@

    An example of scoring software development is presented by 
    Jones \cite{Jones2012}. The methodology looks
    for the presence of various techniques used in software engineering.  
    The methodology provides a score based upon the 
    productivity and quality increase of the technique being evaluated.  
    Points are positive or negative based upon the 
    presense of various techniques. A couple example techniques are: 
    automated source code analysis and continuous integration.  The end 
    result is a score in range $[-10,10]$. 
    While the result is a single number score, it does not account for the 
    entirety of the software development lifecycle.

    Constructive Cost Model (COCOMO) is a software cost estimation model created
    by Boehm \cite{Boehm1981}.  It combines future project characteristics
    with historical project data to create a regression model to estimate the 
    cost of a software project.  The original version developed in 1981 was
    focused on mainframe and batch processing.  An unpdated version, named
    COCOMO II, was created by Boehm in 1995 to be more flexible for newer 
    development practices such as desktop development, off the shelf components,
    and code reuse.  COCOMO provides a nice algorithm for making decisions
    regarding building or buying software products.  It does not provide 
    an algorithm to review and modify past performance 
    based upon estimates.  COCOMO II can be a useful tool for 
    estimating the time and costs within an SDO,
    but it only provides an estimate and not an evaluation of the actual
    performance.

    Sextant is a visualization tool for Java source code \cite{Winter2013}.  
    Sextant provides a graphical representation of the information related 
    to a software system.  The tool provides the capability to provide 
    custom rules which are specific to the domain or application.  However,
    Sextant only provides metrics and analysis of the software code.  
    It provides no information regarding the rest of the 
    software development lifecycle.  Also, the primary output of Sextant 
    is visual graphs.  While these graphs do provide
    useful information, they do not provide a single number 
    to determine the performance of the software.

@@

    Another aspect of software quality is the complexity of the 
    source code.  More complex code results in more maintenance efforts and
    more chances for problems. A couple of numerical measures for the 
    complexity of source code have been created.  The most common examples
    are McCabe \cite{McCabe1976} and Halstead \cite{Halstead1977}.
    However, the measures on source code only explain part of the 
    software development lifecycle.

@@

    Later, Martin Shepperd in \cite{Hassan2013} identified 3 important questions that software
    analytics must address:
    \begin{enumerate}
        \item ``How much better is my model performing than 
            a naive strategy, such as guessing [\ldots]?''
        \item ``How practically significant are the results?''
        \item ``How sensitive are the results to small changes in 
            one or more of the inputs?''
    \end{enumerate}
    These are 3 important questions that should be addressed 
    when presenting any results in software analytics.  The research
    needs to demonstrate clear advantages for practitioners.  The work
    presented in this work will address both the 3 main focus areas and
    the 3 important questions of software analytics.

@@

    After the proper tools are in place to collect the necessary
    data on software development and software analytics are being
    p roperly implemented, an obvious next step is the
    application of gamification to software development. Gamification
    is ``the process of making activities more game-like'' \cite{Werbach2014}.
    Some of the benefits of gamification are higher productivity, competition,
    and greater enjoyment.  
    Prior attempts
    at gamification of software development focus only on 
    the computer programming phase \cite{Snipes2013}. Others
    focus on defining a framework for gamification within
    the software development process \cite{Jain2013}. There are 
    even some indications that gamification might help increase
    software quality \cite{Dubois2013}. 
    While this work will not focus on gamification, it is important to note
    that an implementation of an evaluation technique for software
    development could be implemented simultaneously with a gamification
    strategy. Both will require new collections of data and new reporting.

    Overall, there exist many attempts to 
    evaluate portions of the a software development 
    organization.  None of the the attempts provide
    a single number score for the entirety of the 
    organization.  Most of the techniques focus on
    specific portions of the software development 
    lifecycle, namely the development portion. Plus,
    there are many tools that need to be created for
    software analytics to provide all the value
    that it promises.

@@

    The remainder of this dissertation is divided into 7 chapters.  Chapter 2 provides
    an overview of software, software development life cycles, software engineering, and software
    development organizations.  Chapter 3 introduces some existing techniques for measuring
    an SDO. Chapter 4 then provides an explanation of the Cumulative
    Result Indicator (CRI).  It will present the essential elements for calculating the CRI, as well
    as the formulas, framework, and data necessary to produce the CRI. Chapter 5 provides
    a technological framework for storing the current and historical CRI values.
    Chapter 6 demostrates how CRI can be implemented in a software development portion of 
    a large financial institution. Chapter 7 discusses some possible future directions 
    for further enhancements. Chapter 8 concludes the dissertation with a summary
    of the results.

>>>>

    This dissertation 
    provides a technique for a Software Development Organization (SDO)
    \nomenclature{SDO}{Software Development Organization}to create
    a single number score which indicates the overall performance
    of the organization. The
    score is based upon data collected for 5 key result indicators
    of an SDO: quality, availability,
    satisfaction, schedule, and requirements.  It is not meant
    to be comparative between organizations, but to 
    form a historical baseline for a specific organization.  The single
    number is targeted for upper-level management whom need a quick
    and simple strategy to evaluate the performance of the organization.

@@

    SDOs need a framework to define
    what measurements should be tracked and how those measurements
    should be reported.  The Cumulative Result Indicator (CRI)
    \nomenclature{CRI}{Cumulative Result Indicator}
    framework provides a solid foundation
    for a consistent evaluation.  CRI analyzes the historical performance
    of an SDO
    to create a baseline in order to provide a broad
    view of the overall organization.  It is common for software development
    organizations to measure and focus solely on the source code
    being produced.  However, an SDO does more
    than just produce source code.  There is documentation to be
    written, test cases to be created, systems to be deployed, and
    decisions to be made.  The framework provides an evaluation
    of the overall SDO, not just the
    source code.

@@

        \item[Application] - a software system or a collection of other applications 
        \item[Release] - A collection of projects being put in production on a specified date
        \item[Project] - A body of work involving zero or more applications in preparation for a release 
        \item[SIT] (Systems Integration Testing) - The initial step of testing
            after the development phase of the SDLC.  This is typically 
            performed by members of the SDO.  It is validation that all the
            software components function together as expected.
            \nomenclature{SIT}{Systems Integration Testing} 
        \item[UAT] (User Acceptance Testing) - The final step of testing
            when a select few members of the user group are invited to
            validate the software system. Once validation has occurred for
            UAT, the software system is ready to proceed to production
            \nomenclature{UAT}{User Acceptance Testing} 
        \item[PROD] (Production) - The software has been released to the 
        final audience. \nomenclature{PROD}{Production} 
        \item[defect] ``A software defect is a bug or error that causes
                    software to either stop operating or to produce
                    invalid or unacceptable results'' as quoted from Capers Jones
                \cite{Jones2009}.  It is important to mention that even though defects are typically 
                found in the computer code, a defect should not be isolated to just code.   
                A poorly written requirement or missed test cases can 
                both be considered a defect.  Other common names for a defect 
                are: bug, error, fault, or ticket.
    \end{description}

@@

    \begin{description}
        \item[CMMI MATURITY LEVEL 1 - INITIAL]
            A maturity level 1 organization consists of an
                impromptu and chaotic process.  While working
                products are still produced, the results are 
                often over budget and behind schedule.  A level
                1 organization will also have difficulties 
                repeating a process with the same degree of 
                success.  These organizations typically rely 
                on the heroic efforts of certain individuals.

@@

    A visual description of the CMMI maturity levels can be seen in Figure \ref{fig:cmmi}.  
    While CMMI-Dev does provide an excellent framework for improving a process, it
    is entirely focused on process improvement.  It does not provide guidelines
    for evaluating the final product.  
    Also, it does not provide a specify mechanism for evaluating
    or scoring the progression through the maturity levels.  
    An indicator is still needed to quantify the overall 
    performance of an organization, not
    just the compliance to standard processes.

@@

    An example of scoring software development is presented by 
    Jones \cite{Jones2012}. The methodology looks
    for the presence of various techniques used in software engineering.  
    The methodology provides a score based upon the 
    productivity and quality increase of the technique being evaluated.  
    Points are positive or negative based upon the 
    presence of various techniques. A couple of example techniques are: 
    automated source code analysis and continuous integration.  The end 
    result is a score in range $[-10,10]$. 
    While the result is a single number score, it does not account for the 
    entirety of the software development life cycle.

    Constructive Cost Model (COCOMO) is a software cost estimation model created
    by Boehm \cite{Boehm1981}.  It combines future project characteristics
    with historical project data to create a regression model to estimate the 
    cost of a software project.  The original version developed in 1981 was
    focused on mainframe and batch processing.  An updated version, named
    COCOMO II, was created by Boehm in 1995 to be more flexible for newer 
    development practices such as desktop development, off the shelf components,
    and code reuse.  COCOMO provides a nice algorithm for making decisions
    regarding building or buying software products.  It does not provide 
    an algorithm to review and modify past performance 
    based upon estimates.  COCOMO II can be a useful tool for 
    estimating the time and costs within an SDO,
    but it only provides an estimate and not an evaluation of the actual
    performance.

    Sextant is a visualization tool for Java source code \cite{Winter2013}.  
    Sextant provides a graphical representation of the information related 
    to a software system.  The tool provides the capability to provide 
    custom rules which are specific to the domain or application.  However,
    Sextant only provides metrics and analysis of the software code.  
    It provides no information regarding the rest of the 
    software development life cycle.  Also, the primary output of Sextant 
    is visual graphs.  While these graphs do provide
    useful information, they do not provide a single number 
    to determine the performance of the software.

@@

    Another aspect of software quality is the complexity of the 
    source code.  More complex code results in more maintenance efforts and
    more chances for problems. A couple of numerical measures for the 
    complexity of source code have been created.  The most common examples
    are McCabe \cite{McCabe1976} and Halstead \cite{Halstead1977}.
    However, the measures on source code only explain part of the 
    software development life cycle.

@@

    Later, Martin Shepperd in \cite{Hassan2013} identified 3 important questions that software
    analytics must address:
    \begin{enumerate}
        \item ``How much better is my model performing than 
            a naive strategy, such as guessing [\ldots]?''
        \item ``How practically significant are the results?''
        \item ``How sensitive are the results to small changes in 
            one or more of the inputs?''
    \end{enumerate}
    These are 3 important questions that should be addressed 
    when presenting any results in software analytics.  The research
    needs to demonstrate clear advantages for practitioners.  The work
    presented in this dissertation will address both the 3 main focus areas and
    the 3 important questions of software analytics.

@@

    After the proper tools are in place to collect the necessary
    data on software development and software analytics are being
    properly implemented, an obvious next step is the
    application of gamification to software development. Gamification
    is ``the process of making activities more game-like'' \cite{Werbach2014}.
    Some of the benefits of gamification are higher productivity, competition,
    and greater enjoyment.  
    Prior attempts
    at gamification of software development focus only on 
    the computer programming phase \cite{Snipes2013}. Others
    focus on defining a framework for gamification within
    the software development process \cite{Jain2013}. There are 
    even some indications that gamification might help increase
    software quality \cite{Dubois2013}. 
    While this dissertation will not focus on gamification, it is important to note
    that an implementation of an evaluation technique for software
    development could be implemented simultaneously with a gamification
    strategy. Both will require new collections of data and new reporting.

    Overall, there exist many attempts to 
    evaluate portions of the a software development 
    organization.  None of the the attempts provide
    a single number score for the entirety of the 
    organization.  Most of the techniques focus on
    specific portions of the software development 
    life cycle, namely the development portion. Plus,
    there are many tools that need to be created for
    software analytics to provide all the value
    that it promises.

@@

    The remainder of this dissertation is divided into 7 chapters.  Chapter 2 provides
    an overview of software, software development life cycles, software engineering, and software
    development organizations.  Chapter 3 introduces some existing techniques for measuring
    an SDO. Chapter 4 then provides an explanation of the Cumulative
    Result Indicator (CRI).  It will present the essential elements for calculating the CRI, as well
    as the formulas, framework, and data necessary to produce the CRI. Chapter 5 provides
    a technological framework for storing the current and historical CRI values.
    Chapter 6 demonstrates how CRI can be implemented in a software development portion of 
    a large financial institution. Chapter 7 discusses some possible future directions 
    for further enhancements. Chapter 8 concludes the dissertation with a summary
    of the results.

### 2015-03-18 paper_20_sdo.tex
updates the chapter 1 this work to this dissertation

\subsection{WHAT IS SOFTWARE?}
Numerous definitions can be found for the term \textit{software}.
Software is more than just computer programs. According to Ian Sommerville \cite{Sommerville2001}, 
"Software is not just the programs but also all associated documentation and configuration data which is needed to make these programs operate correctly."
This is the definition used for the remainder of this work.

>>>>

\subsection{WHAT IS SOFTWARE?}
Numerous definitions can be found for the term \textit{software}.
Software is more than just computer programs. According to Ian Sommerville \cite{Sommerville2001}, 
"Software is not just the programs but also all associated documentation and configuration data which is needed to make these programs operate correctly."
This is the definition used for the remainder of this dissertation.

### 2015-03-18 paper_80_conclusion.tex
updates the chapter 1 this work to this dissertation

    There are many metrics that can be used to evaluate a Software
    Development Organization (SDO). The entire SDO needs to be measured 
    and analyzed properly, not just the development portion. 
    Knowing which metrics to use and what they all mean can be a daunting task.  
    This work identified the Cumulative Result Indicator (CRI) which is a
    proposed solution to the difficulty of measuring an SDO by creating a
    single number score for upper-level management to use to quickly gauge
    performance.

    The following have all been provided in this work.
    \begin{itemize}
        \item CRI defines what 5 elements of an SDO should be measured.
            Result indicators are included for quality, availability, satisfaction,
            schedule, and requirements. 
        \item CRI defines what data needs to be collected to create a 
            score for the 5 elements.
        \item CRI defines the formulas to create a score for the 5 elements.
        \item A process was outlined to generate the CRI score.
        \item An SDLC-AE was designed which includes a storage 
            framework for the necessary CRI data.
        \item A comparison with existing SDO evaluation techniques was presented.
        \item Finally, an example CRI score was calculated with data provided by
            an SDO organization within a large financial institution.
    \end{itemize}

>>>>

    There are many metrics that can be used to evaluate a Software
    Development Organization (SDO). The entire SDO needs to be measured 
    and analyzed properly, not just the development portion. 
    Knowing which metrics to use and what they all mean can be a daunting task.  
    This dissertation identified the Cumulative Result Indicator (CRI) which is a
    proposed solution to the difficulty of measuring an SDO by creating a
    single number score for upper-level management to use to quickly gauge
    performance.

    The following have all been provided in this dissertation.
    \begin{itemize}
        \item CRI defines what 5 elements of an SDO should be measured.
            Result indicators are included for quality, availability, satisfaction,
            schedule, and requirements. 
        \item CRI defines what data needs to be collected to create a 
            score for the 5 elements.
        \item CRI defines the formulas to create a score for the 5 elements.
        \item A process was outlined to generate the CRI score.
        \item An SDLC-AE was designed which includes a storage 
            framework for the necessary CRI data.
        \item A comparison with existing SDO evaluation techniques was presented.
        \item Finally, an example CRI score was calculated with data provided by
            an SDO organization within a large financial institution.
    \end{itemize}
